Portal Forecast

### 2018-02-15 evaluation.Rmd
Use longterm controls in website reporting

# Setup rodent observations
species_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  rename(actual = abundance) %>%
  mutate(level='Controls',currency='abundance') %>%
  left_join(new_moons, by='period') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance(shape='flat', level='Controls') %>%
  group_by(period) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='Controls',currency='abundance',species='total') %>%
  left_join(new_moons, by='period')

>>>>

# Setup rodent observations
species_abundance = portalr::abundance(shape='flat', level='treatment', length="longterm") %>%
  filter(treatment=="control") %>%
  rename(actual = abundance, level = treatment) %>%
  mutate(currency='abundance') %>%
  left_join(new_moons, by='period') %>%
  filter(species %in% species_of_interest)

total_abundance = portalr::abundance(shape='flat', level='treatment', length="longterm") %>%
  filter(treatment=="control") %>%
  group_by(period) %>%
  summarise(actual=sum(abundance)) %>%
  ungroup() %>%
  mutate(level='treatment',currency='abundance',species='total') %>%
  left_join(new_moons, by='period')

### 2018-02-15 index.Rmd
Use longterm controls in website reporting

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance("repo")
obs_data$total = rowSums(select(obs_data, -period))
new_moons = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))

@@

for_data = compile_forecasts() %>%
  dplyr::filter(level == 'All', model == 'Ensemble', date == max(date))

@@

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
obs_data = portalr::abundance(level='treatment', length="longterm") %>%
  filter(treatment=="control")
obs_data$total = rowSums(select(obs_data, -c(period, treatment)))
new_moons = read.csv(text = RCurl::getURL("https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv"))

@@

for_data = compile_forecasts() %>%
  dplyr::filter(level == 'Controls', model == 'Ensemble', date == max(date))

@@

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'Contols', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```
